---
title: "FIN580_HW3"
output: pdf_document
---

#installing needed packages
```{r, warning=FALSE,tidy=TRUE, message=FALSE }
#Setup 
library(gridExtra)
library(e1071)
library(lubridate)
library(tidyverse)
library(gridExtra)
library(xlsx)
library(forecast)
library(tseries)
library(stats)
library(car)
library(glmnet)
library(miscTools)
library(Metrics)
library(knitr)
library(class)
library(vars)
library(stargazer)
library(BigVAR)
library(orderedLasso)
library(BioPhysConnectoR)

#Set seed
set.seed(1560)

```
---
  
  Reading in and preprocessing data
```{r, warning=FALSE,tidy=TRUE, message=FALSE }

#setwd("~/Desktop/FIN580/data")
setwd("~/Desktop/Grad_School/2016-2017_Spring/Amin/Homework/HW_3/FIN580/data") #Nina's
load_data_from_scratch = F

if(load_data_from_scratch){
  file_names=dir(path="~/Desktop/FIN580/data",pattern = '.csv')
  currencies = strsplit(file_names[1:(length(file_names)-1)],'USD.csv')
  labels = read.csv(file_names[length(file_names)],header = T)
  labels[,1] = as.Date(labels[,1], origin = lubridate::origin )
  labels[nrow(labels),2] = 0 #not training on last day because do not have data to test fit
  colnames(labels)[1] = "Date"
  
  prices = lapply(file_names[1:length(currencies)], function(x) { 
    temp = read.csv(x ,header = T)
    temp = temp[,c("Date","Close")]
    if(x == "AUDUSD.csv"){
      temp$Date = as.Date(temp$Date, format = "%m/%d/%y",origin = lubridate::origin) #why it has a different format I have no idea
    }
    else{
      temp$Date = as.Date(temp$Date, format = "%m/%d/%Y",origin = lubridate::origin)
    }
    return(temp) })
  
  names(prices) = currencies
  dates = unique(labels[,1])
  
  #compute return series
  get_5min_rets = function(x){
    tot_rets = data.frame(Date=as.Date(character()), Returns = numeric())
    pos = 1
    for(i in 1:length(dates)){
      indicies = which(x[,1] == dates[i])
      if(length(indicies) != 0){
        
        daily_prices = x[indicies,2]
        daily_rets = log(daily_prices[2:length(daily_prices)]/daily_prices[1:(length(daily_prices)-1)])
        len = length(daily_rets)
        tot_rets[pos:(pos+len-1),] = list(rep(dates[i],length(daily_rets)),daily_rets)
        pos = pos + len
      }
    }
    return(tot_rets)
  }
  
  rets_5min = lapply(prices, get_5min_rets)
  
  get_daily_rets = function(x){
    rets = data.frame(Date=as.Date(character()), Ret = numeric(), Train = numeric() )
    pos = 1
    for(i in 1:length(dates)){
      indicies = which(x[,1] == dates[i])
      len = length(indicies)
      if(len != 0){
        ret = log(x[indicies[len],2]/x[indicies[1],2]) #return for the day is log(P_23:55/P_0:00)
        rets[pos,] = list(dates[i],ret, labels[which(labels$Date == dates[i]),2])
        pos = pos + 1
      }
    }
    return(rets)
  }
  
  daily_rets = lapply(prices, get_daily_rets)
  
  
  
  #compute volatility series
  
  get_daily_vols = function(x){
    
    vols = data.frame(Date=as.Date(character()), Vol = numeric(), Train = numeric() )
    pos = 1
    for(i in 1:length(dates)){
      indicies = which(x[,1] == dates[i])
      if(length(indicies) != 0){
        rets = x[indicies,2]
        vol = sqrt(252) * sd(rets) #annualize volatility
        if(vol != 0){ #get rid of days during which vol is 0
          vols[pos,] = list(dates[i],log(vol), labels[which(labels$Date == dates[i]),2])
          pos = pos + 1
        }
      }
    }
    return(vols)
  }
  
  daily_vols = lapply(rets_5min,get_daily_vols)
  
  
  #weekly statics
  dates_by_curr = lapply(daily_vols, function(x){ x$Date}) #which dates have non-zero vols
  
  
  
  get_weekly_vols = function(curr){
    x = rets_5min[[curr]]
    c_dates = dates_by_curr[[curr]]
    
    vols = data.frame(Date=as.Date(character()), Vol = numeric(), Train = numeric() )
    pos = 1
    i = 1
    while(i <= length(c_dates)-5){
      indicies = unique(unlist(sapply(i:(i+4), function(j) { which(x[,1] == c_dates[j])})))
      if(length(indicies) != 0){
        rets = x[indicies,2]
        vol = sqrt(50) * sd(rets) #annualize volatility
        if(vol != 0){ #get rid of days during which vol is 0
          vols[pos,] = list(c_dates[i],log(vol), labels[which(labels$Date == c_dates[i]),2])
          pos = pos + 1
        }
      }
      i = i + 5 
    }
    return(vols)
  }
  
  weekly_vols = lapply(currencies, get_weekly_vols)
  names(weekly_vols) = currencies
  
  
  
  get_weekly_rets = function(curr){
    x = prices[[curr]]
    c_dates = dates_by_curr[[curr]]
    
    rets = data.frame(Date=as.Date(character()), Ret = numeric(), Train = numeric() )
    pos = 1
    i = 1
    while(i <= length(c_dates)-5){
      indicies = unique(unlist(sapply(i:(i+4), function(j) { which(x[,1] == c_dates[j])})))
      n = length(indicies)
      if(n != 0){
        ret = log(x[indicies[n],2] / x[indicies[1],2] )#last day close divided first day open
        rets[pos,] = list(c_dates[i],ret, labels[which(labels$Date == c_dates[i]),2]) 
        pos = pos + 1
      }
      i = i + 5
    }
    return(rets)
  }
  
  weekly_rets = lapply(currencies, get_weekly_rets)
  names(weekly_rets) = currencies
  
  append_target = function(ts){
    for(curr in currencies){
      temp = ts[[curr]]
      len = nrow(ts[[curr]])
      ts[[curr]] = ts[[curr]][1:(len-1),]
      ts[[curr]] [,'Target'] = temp[2:len,2] 
    }
    return(ts)
  }
  
  append_ret = function(ts,rets){
    for(curr in currencies){
      dates = ts[[curr]]$Date
      ret = rets[[curr]]
      pos = 1
      for(d in dates){
        lookup = which(ret[,1]== as.Date(d,lubridate::origin))
        ts[[curr]][pos,'Ret'] = ret$Ret[lookup]
        pos = pos + 1
      }
    }
    return(ts)
  }
  
  append_label = function(ts,rets){
    for(curr in currencies){
      series = ts[[curr]]
      labels = sapply(1:nrow(series),function(i){
        s = sign(series$Target[i] - series$Vol[i])
        if(s == 0){ #break ties
          s = 1
        }
        return(s)} )
      ts[[curr]]['Y(t)'] = labels
    }
    return(ts)
  }
  
  
  daily_data = append_target(daily_vols)
  weekly_data = append_target(weekly_vols)
  daily_data = append_ret(daily_data,daily_rets)
  weekly_data = append_ret(weekly_data,weekly_rets)
  daily_data = append_label(daily_data)
  weekly_data = append_label(weekly_data)
  
  #remove JPY and SEK
  currencies = currencies[-6] 
  currencies = currencies[-8]
  weekly_data = weekly_data[-6]
  weekly_data = weekly_data[-8]
  daily_data = daily_data[-6]
  daily_data = daily_data[-8]
  
  save(weekly_data, file = "weekly_data.Rdata")
  save(daily_data,file = "daily_data.Rdata")
  save(currencies, file = "currencies.RData")
  
  
  
  
}

if(!load_data_from_scratch)  {
  load("weekly_data.Rdata")
  load("daily_data.Rdata")
  load("currencies.RData")
}
```


#SVM implementation

SVM Helper Functions
```{r,tidy=TRUE,warning=FALSE}

#returns the mse from the regression fit using the labels predicted by the svm
get_mse = function(data, pred_labels,indicies,delta){
    sq_errors = sapply(1:length(pred_labels), function(i) {
    if (pred_labels[i] == 1){
      fitted_val = data$Vol[indicies[i]] * (1 + delta)
    }
    else{
      fitted_val = data$Vol[indicies[i]] * (1 - delta)
    }
    return((fitted_val - data$Target[[indicies[i]]])^2)
  })
  return(mean(sq_errors))
}


#inputs is a list of the colnames of data you wish to use eg c('Vol'), kernelType should be either 'radial' or 'linear', k is
cross_validate_svm = function(data,inputs,kernelType){
  train_indicies = which(data$Train == 1)
  test_indicies = which(data$Train == 0)
  
  #set up SVM
  y = as.factor(data$'Y(t)'[train_indicies])
  x_train = vector("list", length(inputs))
  names(x_train) = inputs
  x_test = vector("list", length(inputs))
  names(x_test) = inputs
  for(input in inputs){
    x_train[[input]] = data[train_indicies,input]
    x_test[[input]] = data[test_indicies,input]
  }
  
  x_train = as.data.frame(x_train)
  x_test = as.data.frame(x_test)
  df = x_train
  df['Labels'] = y

#cross-validate svm to find optimal gamma, C
  
  gamma_range = c(1)
  if(kernelType == 'radial'){
   gamma_range = c(.1,.5,1,2) 
  }
  svm_tune = tune(svm, train.x= x_train, train.y= as.factor(df$Labels), kernel=kernelType, ranges=list(cost=10^(-2:1), gamma=gamma_range))
  C_opt = svm_tune$best.model$cost
  gamma_opt = svm_tune$best.model$gamma
  svm_model = svm(as.factor(df$Labels) ~ ., data=df,kernel=kernelType, cost = C_opt, gamma = gamma_opt) 
    
  #predict on training data
  fitted_tr_labels = as.numeric(predict(svm_model,x_train)) #predict entire training set
  fitted_tr_labels[which(fitted_tr_labels == 1)] = -1 #outputs as factor so need to invert 
  fitted_tr_labels[which(fitted_tr_labels == 2)] = 1
  
  #find best delta for the training data with fitted model
  y_vals = data$Target[train_indicies] - data$Vol[train_indicies]
  regressors = fitted_tr_labels * data$Vol[train_indicies]
  ls_fit = lm(y_vals ~ regressors + 0)
  delta_opt = ls_fit$coefficients[1] #delta is non-negative, however we will show results in both cases
  delta_pos = max(delta_opt,0)

  #use delta_opt to compute train and test mses
  train_mse_opt = get_mse(data, fitted_tr_labels,train_indicies,delta_opt)
  train_mse_pos = get_mse(data, fitted_tr_labels,train_indicies,delta_pos)
  
  #accuracy of fit, for sanity check, make sure > 50%
  train_acc = length(which(fitted_tr_labels == data$'Y(t)'[train_indicies]))/length(fitted_tr_labels)
  
  #predict on test
  fitted_test_labels = as.numeric(predict(svm_model,x_test)) #predict entire training set
  fitted_test_labels[which(fitted_test_labels == 1)] = -1 #outputs as factor so need to invert 
  fitted_test_labels[which(fitted_test_labels == 2)] = 1

  #compute test_mse
  test_mse_opt = get_mse(data, fitted_test_labels,test_indicies,delta_opt)
  test_mse_pos = get_mse(data, fitted_test_labels,test_indicies,delta_pos)
  
  #accuracy of fit
  test_acc = length(which(fitted_test_labels == data$'Y(t)'[test_indicies]))/length(fitted_test_labels)
  
  #output results'
  results = data.frame('C' = numeric(),'Gamma' = numeric(),'Train_Acc' = numeric(),'Test_Acc' = numeric(),'Delta_opt' = numeric(), 'Opt_Train_MSE' = numeric(), 'Opt_Test_Mse' = numeric(),'Delta' = numeric(),'Train_MSE' = numeric(), 'Test_MSE' = numeric())
  results[1,] = list(C_opt, gamma_opt,train_acc,test_acc,delta_opt,train_mse_opt,test_mse_opt,delta_pos,train_mse_pos,test_mse_pos)
  return(results)
}

run_svm_regression = function(data,inputs,kernelType){
  results = data.frame('Currency' = character(), 'C' = numeric(), 'Gamma' = numeric() , 'train_Accuracy' = numeric(), 'test_Accuracy' = numeric(), 'Delta_opt' = numeric(), 'Opt_Train_MSE' = numeric(), 'Opt_Test_Mse' = numeric(),  'Delta' = numeric(), 'train_MSE' = numeric(),'test_MSE' = numeric(), stringsAsFactors = F)
  pos = 1
  for(curr in currencies){ 
    temp_results = cross_validate_svm(data[[curr]],inputs,kernelType)
    results[pos,] = list(curr,temp_results[1],temp_results[2],temp_results[3],temp_results[4],temp_results[5],temp_results[6],temp_results[7],temp_results[8],temp_results[9],temp_results[10]) 
    pos = pos + 1
  }
  return(results) 
}


#plotting utility
plot_results = function(results,name_start){
  for(curr in currencies){
    indicies = which(results$Currency == curr)
    name = paste(name_start, 'MSE v Delta for Currency ', curr, sep = "")
    plot(results$Delta[indicies], results$MSE[indicies], xlab = 'Delta', ylab = 'mse',main = name, pch=21,  bg="blue")
    
    index = which.min(results$MSE[indicies])
    points(results$Delta[indicies[index]],results$MSE[indicies[index]] ,pch=21,  bg="red")
    
    dev.copy(pdf,paste(name,".pdf",sep=""))
    dev.off()
    
   name = paste(name_start, 'Accuracy v Delta for Currency ', curr, sep = "")
    plot(results$Delta[indicies], results$Accuracy[indicies], xlab = 'Delta', ylab = 'Accuracy',main = name, pch=21, bg="red")
    index = which.max(results$Accuracy[indicies])
    points(results$Delta[indicies[index]],results$Accuracy[indicies[index]] ,pch=21,  bg="blue")
    
    dev.copy(pdf,paste(name,".pdf",sep=""))
    dev.off()
  }
}

get_cummulative_statics = function(results){
  
  cum_mse = data.frame(Delta = numeric(), MSE = numeric())
  cum_acc = data.frame(Delta = numeric(), Accuracy = numeric())
  
  pos = 1
  for(delta in delta_grid){
    indicies = which(daily_1d_results$Delta == delta)
    cum_mse[pos,] = list(delta, sum(results$MSE[indicies]))
    cum_acc[pos,] = list(delta, mean(results$Accuracy[indicies]))
    pos = pos + 1
  }
  return(c(cum_mse,cum_acc))
}

```



run svm regression 
```{r,tidy=TRUE,warning=FALSE}

daily_1d_results_linear = run_svm_regression(daily_data,c('Vol'), 'linear')
daily_1d_results_rbf = run_svm_regression(daily_data,c('Vol'),'radial') 
daily_2d_results_linear = run_svm_regression(daily_data,c('Vol','Ret'), 'linear')
daily_2d_results_rbf = run_svm_regression(daily_data,c('Vol','Ret'), 'radial')

weekly_1d_results_linear = run_svm_regression(weekly_data,c('Vol'), 'linear')
weekly_1d_results_rbf = run_svm_regression(weekly_data,c('Vol'),'radial') 
weekly_2d_results_linear = run_svm_regression(weekly_data,c('Vol','Ret'), 'linear')
weekly_2d_results_rbf = run_svm_regression(weekly_data,c('Vol','Ret'), 'radial')

```


svm regressions involving moving average
```{r}

#appends moving average over p vols and q rets
append_moving_avg = function(ts,p,q){
  if(q != 0){
    m_avg = data.frame('Date'=as.Date(character()), 'Vol' = numeric(), 'Train' = numeric(), 'Target' = numeric(), 'Ret' = numeric(), 'Y(t)' = numeric(), 'maVol' = numeric(),  maRet = numeric())
    pos = 1
    start = max(p,q)
    for(i in start:nrow(ts)){
      avgVol = mean(ts[(i-p+1):i,'Vol'])
      avgRet = mean(ts[(i-q+1):i,'Ret'])
      m_avg[pos,] = list(as.Date(ts[i,'Date']), ts[i,'Vol'], ts[i,'Train'], ts[i,'Target'], ts[i,'Ret'], ts[i,'Y(t)'],avgVol, avgRet)
      pos = pos + 1
    }
  }
  else{
    m_avg = data.frame('Date'=as.Date(character()), 'Vol' = numeric(), 'Train' = numeric(), 'Target' = numeric(), 'Ret' = numeric(), 'Y(t)' = numeric(), 'maVol' = numeric())
    pos = 1
    start = max(p,q)
    for(i in start:nrow(ts)){
      avgVol = mean(ts[(i-p+1):i,'Vol'])
      m_avg[pos,] = list(as.Date(ts[i,'Date']), ts[i,'Vol'], ts[i,'Train'], ts[i,'Target'], ts[i,'Ret'], ts[i,'Y(t)'],avgVol)
      pos = pos + 1
    }
  }
  colnames(m_avg)[1:6] = colnames(daily_data[['AUD']])
  return(m_avg)
}

run_svm_moving_avg = function(data,kernelType){
  look_back_p = c(3,5,10)
  look_back_q = c(0,3,5,10)
  results = data.frame('Currency' = character(), 'p' = numeric(), 'q' = numeric(), 'C' = numeric(), 'Gamma' = numeric() , 'train_Accuracy' = numeric(), 'test_Accuracy' = numeric(), 'Delta_opt' = numeric(), 'Opt_Train_MSE' = numeric(), 'Opt_Test_Mse' = numeric(),  'Delta' = numeric(), 'train_MSE' = numeric(),'test_MSE' = numeric(), stringsAsFactors = F)
  
  pos = 1
  for(curr in currencies){ 
    for(p in look_back_p){
      for(q in look_back_q){
        
        if(q == 0){
          inputs = c('maVol')
        }
        else{
          inputs = c('maVol','maRet')
        }
        
        curr_data = append_moving_avg(data[[curr]],p,q)
        temp_results = cross_validate_svm(curr_data,inputs,kernelType)
        results[pos,] = list(curr,p,q,temp_results[1],temp_results[2],temp_results[3],temp_results[4],temp_results[5],temp_results[6],temp_results[7],temp_results[8],temp_results[9],temp_results[10]) 
    pos = pos + 1
      }
    }
  }
  return(results) 
}

daily_ma_results_linear = run_svm_moving_avg(daily_data,'linear')
daily_ma_results_rbf = run_svm_moving_avg(daily_data,'radial')
weekly_ma_results_linear = run_svm_moving_avg(weekly_data,'linear')
weekly_ma_results_rbf = run_svm_moving_avg(weekly_data,'radial')

```


Compile results
```{r}
#helper functions
#get_best_results = function(data){
  results = data.frame(Currency = character(), train_Accuracy = numeric(), test_Accuracy = numeric(), Train_MSE = numeric(), test_MSE = numeric(), stringsAsFactors = F )
    pos = 1
    for(curr in currencies){
      indicies = which(data$Currency == curr)
      winner = data[which.max(data$train_Accuracy[indicies]),] #decision criterion, choose p,q that maximize train_Accuracy, issues with constant delta = 0 prevents train_MSE from being good decision

      results[pos,] = list(curr,winner['train_Accuracy'],winner['test_Accuracy'],winner['Opt_Train_MSE'],winner['Opt_Test_Mse'])
      pos = pos + 1
    }
    return(results)
}

get_best_ma_results = function(data){
    results = data.frame(Currency = character(), p = numeric(), q = numeric(), train_Accuracy = numeric(), test_Accuracy = numeric(), Train_MSE = numeric(), test_MSE = numeric(), stringsAsFactors = F )
    pos = 1
    for(curr in currencies){
      indicies = which(data$Currency == curr)
      winner = data[which.max(data$train_Accuracy[indicies]),] #decision criterion, choose p,q that maximize train_Accuracy, issues with constant delta = 0 prevents train_MSE from being good decision

      results[pos,] = list(curr,winner['p'],winner['q'],winner['train_Accuracy'],winner['test_Accuracy'],winner['Opt_Train_MSE'],winner['Opt_Test_Mse'])
      pos = pos + 1
    }
    return(results)
  }

  
  #best performers on moving average data
daily_best_ma_results_linear = get_best_ma_results(daily_ma_results_linear)
daily_best_ma_results_rbg = get_best_ma_results(daily_ma_results_rbf)
weekly_best_ma_results_linear = get_best_ma_results(weekly_ma_results_linear)
weekly_best_ma_results_rbg = get_best_ma_results(weekly_ma_results_rbf)

```


Plots and Analysis
```{r}
methods = c('y(vol) linear','y(vol) rbf','y(vol,ret) linear','y(vol,ret) rbf', 'y(E_p(vol),E_q(vol)) linear','y(E_p(vol),E_q(vol)) rbf')




daily_results = list(daily_1d_results_linear, daily_1d_results_rbf, daily_2d_results_linear,daily_2d_results_rbf,daily_best_ma_results_linear, daily_best_ma_results_rbg)

weekly_results = list(weekly_1d_results_linear, weekly_1d_results_rbf, weekly_2d_results_linear,weekly_2d_results_rbf,weekly_best_ma_results_linear, weekly_best_ma_results_rbg)


#Compilation function
compile_accuracy = function(data){
  tr_acc = rep(0,length(data))
  test_acc = rep(0,length(data))
  for(i in 1:length(data)){
    result = data[[i]]
    for(curr in currencies){
      index = which(result$Currency == curr)
      if(i < 5){
        tr_acc[i] = tr_acc[i] + as.numeric(result[index,'train_Accuracy'])
        test_acc[i] = test_acc[i] + as.numeric(result[index,'test_Accuracy'])
      }
      else{
        tr_acc[i] = tr_acc[i] + as.numeric(result[index,'train_Accuracy'][[1]])
        test_acc[i] = test_acc[i] + as.numeric(result[index,'test_Accuracy'][[1]])
      }
    }
    tr_acc[i] = tr_acc[i]/ length(currencies)
    test_acc[i] = test_acc[i]/ length(currencies)
  }
  return(list(tr_acc,test_acc))
}


compile_mse = function(data){
  tr_mse = rep(0,length(data))
  test_mse = rep(0,length(data))
  for(i in 1:length(data)){
    result = data[[i]]
    for(curr in currencies){
      index = which(result$Currency == curr)
      if(i < 5){
        tr_mse[i] = tr_mse[i] + as.numeric(result[index,7])
        test_mse[i] = test_mse[i] + as.numeric(result[index,8])
      }
      else{
        tr_mse[i] = tr_mse[i] + as.numeric(result[index,6][[1]])
        test_mse[i] = test_mse[i] + as.numeric(result[index,7][[1]])
      }
    }
    tr_mse[i] = tr_mse[i]/ length(currencies)
    test_mse[i] = test_mse[i]/ length(currencies)
  }
  return(list(tr_mse,test_mse))
  
}



#Accuracy Plots

setwd("~/Desktop/FIN580/hw3/Plots/AggResults")

acc_results = compile_accuracy(daily_results)
daily_tr_acc = acc_results[[1]]
  daily_test_acc = acc_results[[2]]
name = 'Aggregate Training Accuracy for Forecasting Daily Vol '
barplot(daily_tr_acc, main=name, horiz=F, names.arg= methods, cex.names=0.42, xlab = 'Method', ylab = 'Accuracy', col=c("darkblue","red","cyan","orange","magenta", "purple"))
dev.copy(pdf,paste(name,".pdf",sep=""))
dev.off()


name = 'Aggregate Testing Accuracy for Forecasting Daily Vol '
barplot(daily_test_acc, main=name, horiz=F, names.arg= methods, cex.names=0.42, xlab = 'Method', ylab = 'Accuracy', col=c("darkblue","red","cyan","orange","magenta", "purple"))
dev.copy(pdf,paste(name,".pdf",sep=""))
dev.off()


acc_results = compile_accuracy(weekly_results)
weekly_tr_acc = acc_results[[1]]
weekly_test_acc = acc_results[[2]]
name = 'Aggregate Training Accuracy for Forecasting Weekly Vol '
barplot(weekly_tr_acc, main=name, horiz=F, names.arg= methods, cex.names=0.42, xlab = 'Method', ylab = 'Accuracy', col=c("darkblue","red","cyan","orange","magenta", "purple"))
dev.copy(pdf,paste(name,".pdf",sep=""))
dev.off()


name = 'Aggregate Testing Accuracy for Forecasting Weekly Vol '
barplot(weekly_test_acc, main=name, horiz=F, names.arg= methods, cex.names=0.42, xlab = 'Method', ylab = 'Accuracy', col=c("darkblue","red","cyan","orange","magenta", "purple"))
dev.copy(pdf,paste(name,".pdf",sep=""))
dev.off()


#MSE Plots
mse_results = compile_mse(daily_results)
daily_tr_mse = mse_results[[1]]
daily_test_mse = mse_results[[2]]

name = 'Aggregate Training MSE for Forecasting Daily Vol '
barplot(daily_tr_mse, main=name, horiz=F, names.arg= methods, cex.names=0.42, xlab = 'Method', ylab = 'Accuracy', col=c("darkblue","red","cyan","orange","magenta", "purple"))
dev.copy(pdf,paste(name,".pdf",sep=""))
dev.off()


name = 'Aggregate Testing MSE for Forecasting Daily Vol '
barplot(daily_test_mse, main=name, horiz=F, names.arg= methods, cex.names=0.42, xlab = 'Method', ylab = 'Accuracy', col=c("darkblue","red","cyan","orange","magenta", "purple"))
dev.copy(pdf,paste(name,".pdf",sep=""))
dev.off()

mse_results = compile_mse(weekly_results)
weekly_tr_mse = mse_results[[1]]
weekly_test_mse = mse_results[[2]]

name = 'Aggregate Training MSE for Forecasting Weekly Vol '
barplot(weekly_tr_mse, main=name, horiz=F, names.arg= methods, cex.names=0.42, xlab = 'Method', ylab = 'Accuracy', col=c("darkblue","red","cyan","orange","magenta", "purple"))
dev.copy(pdf,paste(name,".pdf",sep=""))
dev.off()

name = 'Aggregate Testing MSE for Forecasting Weekly Vol '
barplot(weekly_test_mse, main=name, horiz=F, names.arg= methods, cex.names=0.42, xlab = 'Method', ylab = 'Accuracy', col=c("darkblue","red","cyan","orange","magenta", "purple"))
dev.copy(pdf,paste(name,".pdf",sep=""))
dev.off()



```




#Logistic Regression Implementation
Data getting function for LR 
```{r,tidy=TRUE,warning=FALSE}

rm(list = ls())
load("daily_vols.RData")
load("weekly_vols.RData")
load("daily_rets.RData")
load("weekly_rets.RData")
load("currencies.RData")


#data name is "daily" or "weekly", i is numeric, train is 1 (for true) or 0 (for false), add_rt is also 1 (for true) or 0 (for false)
get_lr_data=function(data_name,i,train,add_rt){
  use_data=get(paste(data_name,"_vols",sep=""))
  use_data=use_data[[i]]
  t1_indices=which(use_data[,"Train"]==train)
  t_indices=t1_indices-1
  if(add_rt>0){
    rt=get(paste(data_name,"_rets",sep=""))
    rt=rt[[i]]
    ret_data=data.frame(matrix(cbind(use_data[t1_indices,"Vol"],use_data[t_indices,"Vol"],rt[t_indices,"Ret"]),ncol=3))
    colnames(ret_data)=c("t1","t","rt")
  }
  else{
    ret_data=data.frame(matrix(cbind(use_data[t1_indices,"Vol"],use_data[t_indices,"Vol"]),ncol=2))
    colnames(ret_data)=c("t1","t")
  }
  
  return(ret_data)
} 

#data name is "daily" or "weekly", i is numeric, train is 1 (for true) or 0 (for false), add_rt is also 1 (for true) or 0 (for false)
#p and q are for MA terms
get_lr_data_pq=function(data_name,i,train,add_rt,p,q){
  use_data=get(paste(data_name,"_vols",sep=""))
  use_data=use_data[[i]]
  t1_indices=which(use_data[,"Train"]==train)
  ept=sapply(t1_indices,function(i){
    start_i=max(i-p-2,0)+1
    return(mean(use_data[start_i:(i-1),"Vol"]))
  })
  if(add_rt>0){
    rt=get(paste(data_name,"_rets",sep=""))
    rt=rt[[i]]
    eqrt=sapply(t1_indices,function(i){
      start_i=max(i-q-2,0)+1
      return(mean(rt[start_i:(i-1),"Ret"]))
    })
    ret_data=data.frame(matrix(cbind(use_data[t1_indices,"Vol"],ept,eqrt),ncol=3))
    colnames(ret_data)=c("t1","ept","eqrt")
  }
  else{
    ret_data=data.frame(matrix(cbind(use_data[t1_indices,"Vol"],ept),ncol=2))
    colnames(ret_data)=c("t1","ept")
  }
  return(ret_data)
} 

```

Model fitting and mses
Logistic regression - Model 1
```{r,tidy=TRUE,warning=FALSE}
#Optimization of delta for logistic regression over training set
#Fit model for one currency for one delta
#New_data is for prediction
fit_lr=function(use_data,delta,new_data){
  y=sapply(seq(1,nrow(use_data),1), function(i){ 
    if(use_data[i,"t1"]/use_data[i,"t"]-1 >= delta){
      return(1)
    }
    else{
      return(0) #glm() uses 1 or 0 shouldnt matter since we already labeled y based on its being -1 or 1
    }})
  use_data=cbind(y,use_data,use_data[,"t"]*delta)
  colnames(use_data)=c(colnames(use_data[,1:3]),"t1del")
  model=glm(formula=as.formula("y~(t1-t)/(t1del)"),family=binomial(link="logit"),data=use_data)
  new_data=cbind(use_data,use_data[,"t"]*delta)
  pred_y=predict(model,type="response",newdata=new_data)
  pred_sigs=sapply(seq(1,length(y),1),function(i){
    if(round(y[i],0)==1){
      return(new_data[i,"t"]*(1+delta))
    }
    else{
      return(new_data[i,"t"]*(1-delta))
    }
  } )
  return(mse(pred_sigs,new_data[,"t1"]))
}

#Sequence of deltas to use
deltas=seq(0,0.15,length.out=10)
#Will save mse by delta by currency just in case we want to get fancy and plot that, but probs not gonna happen tbh 
mses_d=data.frame(matrix(NA,ncol=length(currencies),nrow=length(deltas)))
colnames(mses_d)=currencies
rownames(mses_d)=round(deltas,2)
mses_w=data.frame(matrix(NA,ncol=length(currencies),nrow=length(deltas)))
colnames(mses_w)=currencies
rownames(mses_w)=round(deltas,2)
#Daily - train
for(i in 1:length(currencies)){
  u_d=get_lr_data("daily",i,1,0)
  mses_d[,i]=sapply(deltas,function(x){fit_lr(u_d,x,u_d)}) #newdata = usedata=train
}

min_del_d=deltas[which.min(rowMeans(mses_d))]

#Weekly - train
for(i in 1:length(currencies)){
  u_d=get_lr_data("weekly",i,1,0)
  mses_w[,i]=sapply(deltas,function(x){fit_lr(u_d,x,u_d)}) #newdata = usedata=train
}
min_del_w=deltas[which.min(rowMeans(mses_w))]

stargazer(mses_d,summary=FALSE)
stargazer(mses_w,summary=FALSE)

#Plot MSES vs. Delta - training data
plot(deltas,rowMeans(mses_d),pch=23,col=2,main="Training MSE by Delta - Daily Vols",xlab="Delta",ylab="MSE over training data")
dev.copy(pdf,"lr_daily_train.pdf")
dev.off()
plot(deltas,rowMeans(mses_w),pch=2,col=3,main="Training MSE by Delta - Weekly Vols",xlab="Delta",ylab="MSE over training data")
dev.copy(pdf,"lr_weekly_train.pdf")
dev.off()

#Testing mses - we'll combine weekly and daily
mses_test=data.frame(matrix(NA,ncol=length(currencies)+1,nrow=2))
colnames(mses_test)=c(currencies,"Average")
rownames(mses_test)=c("Daily Testing","Weekly Testing")
for(i in 1:length(currencies)){
  u_d=get_lr_data("daily",i,1,0)
  n_d=get_lr_data("daily",i,0,0)
  mses_test[1,i]=fit_lr(u_d,min_del_d,n_d)
  u_d=get_lr_data("weekly",i,1,0)
  n_d=get_lr_data("weekly",i,0,0)
  mses_test[2,i]=fit_lr(u_d,min_del_w,n_d)
}
mses_test[,ncol(mses_test)]=rowMeans(mses_test[,1:9])
stargazer(t(mses_test),summary=FALSE,rownames=TRUE)

```


Logistic regression - Model 2
```{r,tidy=TRUE,warning=FALSE}
#Optimization of delta for logistic regression over training set
#Fit model for one currency for one delta
#New_data is for prediction
fit_lr_2=function(use_data,delta,new_data){
  y=sapply(seq(1,nrow(use_data),1), function(i){ 
    if((use_data[i,"t1"]-use_data[i,"rt"])/use_data[i,"t"]-1 >= delta){
      return(1)
    }
    else{
      return(0) #glm() uses 1 or 0 shouldnt matter since we already labeled y based on its being -1 or 1
    }})
  use_data=cbind(y,use_data,use_data[,"t"]*delta)
  colnames(use_data)=c(colnames(use_data[,1:4]),"t1del")
  model=glm(formula=as.formula("y~(t1-rt-t)/(t1del)"),family=binomial(link="logit"),data=use_data)
  new_data=cbind(use_data,use_data[,"t"]*delta)
  pred_y=predict(model,type="response",newdata=new_data)
  pred_sigs=sapply(seq(1,length(y),1),function(i){
    if(round(y[i],0)==1){
      return(new_data[i,"rt"]+new_data[i,"t"]*(1+delta))
    }
    else{
      return(new_data[i,"rt"]+new_data[i,"t"]*(1-delta))
    }
  } )
  return(mse(pred_sigs,new_data[,"t1"]))
}

#Sequence of deltas to use
deltas=seq(0,0.15,length.out=10)
#Will save mse by delta by currency just in case we want to get fancy and plot that, but probs not gonna happen tbh 
mses_d=data.frame(matrix(NA,ncol=length(currencies),nrow=length(deltas)))
colnames(mses_d)=currencies
rownames(mses_d)=round(deltas,2)
mses_w=data.frame(matrix(NA,ncol=length(currencies),nrow=length(deltas)))
colnames(mses_w)=currencies
rownames(mses_w)=round(deltas,2)
#Daily - train
for(i in 1:length(currencies)){
  u_d=get_lr_data("daily",i,1,1)
  mses_d[,i]=sapply(deltas,function(x){fit_lr_2(u_d,x,u_d)}) #newdata = usedata=train
}

min_del_d=deltas[which.min(rowMeans(mses_d))]

#Weekly - train
for(i in 1:length(currencies)){
  u_d=get_lr_data("weekly",i,1,1)
  mses_w[,i]=sapply(deltas,function(x){fit_lr_2(u_d,x,u_d)}) #newdata = usedata=train
}

min_del_w=deltas[which.min(rowMeans(mses_w))]

stargazer(mses_d,summary=FALSE)
stargazer(mses_w,summary=FALSE)

#Plot MSES vs. Delta - training data
plot(deltas,rowMeans(mses_d),pch=23,col=2,main="Forecaster 2: Training MSE by Delta - Daily Vols",xlab="Delta",ylab="MSE over training data")
dev.copy(pdf,"lr_daily_train_2.pdf")
dev.off()
plot(deltas,rowMeans(mses_w),pch=2,col=3,main="Forecaster 2: Training MSE by Delta - Weekly Vols",xlab="Delta",ylab="MSE over training data")
dev.copy(pdf,"lr_weekly_train_2.pdf")
dev.off()

#Testing mses - we'll combine weekly and daily
mses_test=data.frame(matrix(NA,ncol=length(currencies)+1,nrow=2))
colnames(mses_test)=c(currencies,"Average")
rownames(mses_test)=c("Daily Testing","Weekly Testing")
for(i in 1:length(currencies)){
  u_d=get_lr_data("daily",i,1,1)
  n_d=get_lr_data("daily",i,0,1)
  mses_test[1,i]=fit_lr(u_d,min_del_d,n_d)
  u_d=get_lr_data("weekly",i,1,0)
  n_d=get_lr_data("weekly",i,0,0)
  mses_test[2,i]=fit_lr(u_d,min_del_w,n_d)
}
mses_test[,ncol(mses_test)]=rowMeans(mses_test[,1:9])
stargazer(t(mses_test),summary=FALSE,rownames=TRUE)
```

Logistic regression - Model 3 
```{r,tidy=TRUE,warning=FALSE}
#Optimization of delta for logistic regression over training set
#Fit model for one currency for one delta
#New_data is for prediction
fit_lr_3=function(use_data,delta,new_data,p){
  y=sapply(seq(1,nrow(use_data),1), function(i){ 
    if((use_data[i,"t1"])/use_data[i,"ept"]-1 >= delta){
      return(1)
    }
    else{
      return(0) #glm() uses 1 or 0 shouldnt matter since we already labeled y based on its being -1 or 1
    }})
  use_data=cbind(y,use_data,use_data[,"ept"]*delta)
  colnames(use_data)=c(colnames(use_data[,1:3]),"eptdel")
  model=glm(formula=as.formula("y~(t1-ept)/(eptdel)"),family=binomial(link="logit"),data=use_data)
  new_data=cbind(use_data,use_data[,"ept"]*delta)
  pred_y=predict(model,type="response",newdata=new_data)
  pred_sigs=sapply(seq(1,length(y),1),function(i){
    if(round(y[i],0)==1){
      return(new_data[i,"ept"]*(1+delta))
    }
    else{
      return(new_data[i,"ept"]*(1-delta))
    }
  } )
  return(mse(pred_sigs,new_data[,"t1"]))
}

#Sequence of deltas to use
deltas=seq(0,0.15,length.out=10)
ps=c(3,5,10)
#Will save mse by delta by currency just in case we want to get fancy and plot that, but probs not gonna happen tbh 
#To save memory - I manually change p and re-run to avoid saving down too many new tables and crashing R
p=10
mses_d=data.frame(matrix(NA,ncol=length(currencies),nrow=length(deltas)))
colnames(mses_d)=currencies
rownames(mses_d)=round(deltas,2)
mses_w=data.frame(matrix(NA,ncol=length(currencies),nrow=length(deltas)))
colnames(mses_w)=currencies
rownames(mses_w)=round(deltas,2)
#Daily - train
for(i in 1:length(currencies)){
  u_d=get_lr_data_pq("daily",i,1,0,p,1) #q does't matter if no rt
  mses_d[,i]=sapply(deltas,function(x){fit_lr_3(u_d,x,u_d,p)}) #newdata = usedata=train
}

min_3_d=min(rowMeans(mses_d))
min_del_d_3=deltas[which.min(rowMeans(mses_d))]

min_5_d=min(rowMeans(mses_d))
min_del_d_5=deltas[which.min(rowMeans(mses_d))]

min_10_d=min(rowMeans(mses_d))
min_del_d_10=deltas[which.min(rowMeans(mses_d))]

#Weekly - train
for(i in 1:length(currencies)){
  u_d=get_lr_data_pq("weekly",i,1,0,p,1)
  mses_w[,i]=sapply(deltas,function(x){fit_lr_3(u_d,x,u_d,p)}) #newdata = usedata=train
}

min_3_w=min(rowMeans(mses_w))
min_del_w_3=deltas[which.min(rowMeans(mses_w))]

min_5_w=min(rowMeans(mses_w))
min_del_w_5=deltas[which.min(rowMeans(mses_w))]

min_10_w=min(rowMeans(mses_w))
min_del_w_10=deltas[which.min(rowMeans(mses_w))]

stargazer(mses_d,summary=FALSE)
stargazer(mses_w,summary=FALSE)

#Plot MSES vs. Delta - training data
plot(deltas,rowMeans(mses_d),pch=23,col=2,main="Forecaster 3: Training MSE by Delta - Daily Vols - p=10",xlab="Delta",ylab="MSE over training data")
dev.copy(pdf,"lr_daily_train_3_10.pdf")
dev.off()
plot(deltas,rowMeans(mses_w),pch=2,col=3,main="Forecaster 3: Training MSE by Delta - Weekly Vols - p=10",xlab="Delta",ylab="MSE over training data")
dev.copy(pdf,"lr_weekly_train_3_10.pdf")
dev.off()

#Testing mses - we'll combine weekly and daily into one table
p_opt_d=ps[which.min(c(min_3_d,min_5_d,min_10_d))] #p=5
del_opt_d=deltas[which.min(c(min_del_d_3,min_del_d_5,min_del_d_10))]
p_opt_w=ps[which.min(c(min_3_w,min_5_w,min_10_w))] #p=3
del_opt_w=deltas[which.min(c(min_del_w_3,min_del_w_5,min_del_w_10))]
mses_test=data.frame(matrix(NA,ncol=length(currencies)+1,nrow=2))
colnames(mses_test)=c(currencies,"Average")
rownames(mses_test)=c("Daily Testing p=5","Weekly Testing p=3")
for(i in 1:length(currencies)){
  u_d=get_lr_data_pq("daily",i,1,0,p_opt_d,1)
  n_d=get_lr_data_pq("daily",i,0,0,p_opt_d,1)
  mses_test[1,i]=fit_lr_3(u_d,del_opt_d,n_d,p_opt_d)
  u_d=get_lr_data_pq("weekly",i,1,0,p_opt_w,1)
  n_d=get_lr_data_pq("weekly",i,0,0,p_opt_w,1)
  mses_test[2,i]=fit_lr_3(u_d,del_opt_w,n_d,p_opt_w)
}
mses_test[,ncol(mses_test)]=rowMeans(mses_test[,1:9])
stargazer(t(mses_test),summary=FALSE,rownames=TRUE)

```

Logistic regression - Model 4
```{r,tidy=TRUE,warning=FALSE}
#Optimization of delta for logistic regression over training set
#Fit model for one currency for one delta
#New_data is for prediction
fit_lr_4=function(use_data,delta,new_data,p,q){
  y=sapply(seq(1,nrow(use_data),1), function(i){ 
    if((use_data[i,"t1"]-use_data[i,"eqrt"])/use_data[i,"ept"]-1 >= delta){
      return(1)
    }
    else{
      return(0) #glm() uses 1 or 0 shouldnt matter since we already labeled y based on its being -1 or 1
    }})
  use_data=cbind(y,use_data,use_data[,"ept"]*delta)
  colnames(use_data)=c(colnames(use_data[,1:4]),"eptdel")
  model=glm(formula=as.formula("y~(t1-eqrt-ept)/(eptdel)"),family=binomial(link="logit"),data=use_data)
  new_data=cbind(use_data,use_data[,"ept"]*delta)
  pred_y=predict(model,type="response",newdata=new_data)
  pred_sigs=sapply(seq(1,length(y),1),function(i){
    if(round(y[i],0)==1){
      return(new_data[i,"eqrt"]+new_data[i,"ept"]*(1+delta))
    }
    else{
      return(new_data[i,"eqrt"]+new_data[i,"ept"]*(1-delta))
    }
  } )
  return(mse(pred_sigs,new_data[,"t1"]))
}
#Note we will not be outputting all 18 combination of daily/weekly, ps , and qs just the optimal
#Optimizing
qs=ps
mses_d=data.frame(matrix(NA,ncol=length(currencies),nrow=length(deltas)))
colnames(mses_d)=currencies
rownames(mses_d)=round(deltas,2)
mses_w=data.frame(matrix(NA,ncol=length(currencies),nrow=length(deltas)))
colnames(mses_w)=currencies
rownames(mses_w)=round(deltas,2)
min_d=100000
min_w=100000

for(k in 1:length(ps)){
  print(paste("p",ps[k]))
  for(j in 1:length(qs)){
    print(paste("q",qs[j]))
    for(i in 1:length(currencies)){
      u_d=get_lr_data_pq("daily",i,1,1,ps[k],qs[j]) 
      mses_d[,i]=sapply(deltas,function(x){fit_lr_4(u_d,x,u_d,p,q)})
      u_d=get_lr_data_pq("weekly",i,1,1,ps[k],qs[j])
      mses_w[,i]=sapply(deltas,function(x){fit_lr_4(u_d,x,u_d,p,q)})
    }
    #Check for new min
    if(min(rowMeans(mses_d))<min_d){
      i_d=which.min(rowMeans(mses_d))
      del_opt_d=deltas[i_d]
      p_opt_d=ps[k]
      q_opt_d=qs[j]
      min_d=min(rowMeans(mses_d))
    }
    if(min(rowMeans(mses_w))<min_w){
      i_w=which.min(rowMeans(mses_w))
      del_opt_w=deltas[i_w]
      p_opt_w=ps[k]
      q_opt_w=qs[j]
      min_w=min(rowMeans(mses_w))
    }
  }
}

#Run on testing data w optimal parameters
mses_test=data.frame(matrix(NA,ncol=length(currencies)+1,nrow=2))
colnames(mses_test)=c(currencies,"Average")
rownames(mses_test)=c(paste("Daily Testing",round(del_opt_d,3),p_opt_d,q_opt_d),paste("Weekly Testing",round(del_opt_w,3),p_opt_w,q_opt_w))
for(i in 1:length(currencies)){
  u_d=get_lr_data_pq("daily",i,1,1,p_opt_d,q_opt_d)
  n_d=get_lr_data_pq("daily",i,0,1,p_opt_d,q_opt_d)
  mses_test[1,i]=fit_lr_4(u_d,del_opt_d,n_d,p_opt_d,q_opt_w)
  u_d=get_lr_data_pq("weekly",i,1,1,p_opt_w,q_opt_w)
  n_d=get_lr_data_pq("weekly",i,0,1,p_opt_w,q_opt_w)
  mses_test[2,i]=fit_lr_4(u_d,del_opt_w,n_d,p_opt_w,q_opt_w)
}
mses_test[,ncol(mses_test)]=rowMeans(mses_test[,1:9])
stargazer(t(mses_test),summary=FALSE,rownames=TRUE)





```