---
title: "Gnedin_Perlen_Final_Revised"
author: "Chase Perlen"
date: "April 24, 2017"
output: pdf_document
---


#installing needed packages
```{r, warning=FALSE,tidy=TRUE, message=FALSE }
#Setup 
library(xlsx)
library(forecast)
library(tseries)
library(stats)
library(car)
library(glmnet)
library(miscTools)
library(Metrics)
library(knitr)
library(class)
library(vars)
library(stargazer)
library(fGarch)
library(orderedLasso)
library(depmixS4)

#Set seed
set.seed(1560)

```
---
  
Loading data 
```{r, warning=FALSE,tidy=TRUE, message=FALSE }
setwd("~/Desktop/FIN580_Final")
load("daily_data.RData")
load("weekly_data.RData")
load("currencies.RData")

#update data for this project
update_data = function(data){
  for(curr in currencies){
    curr_data = data[[curr]]
    curr_data = curr_data[,c('Date','Vol','Target','Ret')]
    n = nrow(curr_data)
    S_train = c(rep(1,floor(n*(3/5))),rep(0,n-floor(n*3/5)))
    curr_data[,'S_train'] = S_train 
    data[[curr]] = curr_data
  }
  return(data)
}

daily_data = update_data(daily_data)
weekly_data = update_data(weekly_data)

```


Part 1: Baseline results

We start by fitting random walk, Garch, and ordered Lasso without HMM as basis for comparison

Fit Random Walk
```{r, warning=FALSE,tidy=TRUE, message=FALSE }
rand_walk = function(data){
  tr_indicies = which(data$S_train == 1)
  test_indicies = which(data$S_train == 0)
  
  tr_mse = rep(0,length(currencies)) 
  test_mse = rep(0,length(currencies)) 
  
  for(curr in 1:length(currencies)){
    vols = data[[curr]]$Vol
    next_vol = data[[curr]]$Target
    in_train = data[[curr]]$S_train
      
    num_train = 0
    num_test = 0
    for(i in 1:length(vols)){
      if(in_train[i] == 1){
        tr_mse[curr] =  tr_mse[curr] + (vols[i] - next_vol[i])^2
        num_train = num_train + 1
      }
      else{
        test_mse[curr] =  test_mse[curr] + (vols[i] - next_vol[i])^2
        num_test = num_test + 1
      }
    }
    tr_mse[curr] = tr_mse[curr] / num_train
    test_mse[curr] = test_mse[curr] / num_test
  }
  return(c(mean(tr_mse),mean(test_mse)))
}

daily_rw = rand_walk(daily_data)
weekly_rw = rand_walk(weekly_data)
  
rw_mse = matrix(nrow = 2, ncol = 2)
colnames(rw_mse) = c('Train','Test')
rownames(rw_mse) = c('Daily','Weekly')

rw_mse[1,] = daily_rw
rw_mse[2,] = weekly_rw

stargazer(rw_mse)

```

Fit GARCH

```{r, warning=FALSE,tidy=TRUE, message=FALSE }


garch_stats=function(data_type,curr_i){ 
  use_data=get(paste(data_type,"_data",sep=""))[[curr_i]]
  train_ret=use_data[which(use_data[,"S_train"]==1),"Ret"]
  test_ret = use_data[which(use_data[,"S_train"]==0),"Ret"]
  test_vol= use_data[which(use_data[,"S_train"]==0),"Target"]
  pred_y = rep(0,length(test_ret))

  for(i in 1:length(test_ret)){
    model=garchFit(formula=~garch(1,1),data=append(train_ret,test_ret[1:i]),verbose=FALSE)
    pred_y[i]=  predict(model,n.ahead=1)$standardDeviation
  }
  #Since we have log-vols, but the predictions arent need to change
  pred_y=log(pred_y) 
  return(mse(pred_y,test_vol))
}

#Get stats for using just one garch as a baseline comparison
mse_garch_all_daily=sapply(seq(1,length(currencies),1), function(x){ garch_stats("daily",x)})

mse_garch_all_weekly=sapply(seq(1,length(currencies),1), function(x){ garch_stats("weekly",x)})


###REDO THIS
save(mse_garch_all_daily,file="mse_garch_all_daily.RData")
save(mse_garch_all_weekly,file="mse_garch_all_weekly.RData")
#Table for presentation - we will overwrite pres_table consistently throughout
#Tables output into Latex
pres_table=cbind(mse_garch_all_daily,mse_garch_all_weekly)
means=c(mean(mse_garch_all_daily),mean(mse_garch_all_weekly))
pres_table=rbind(pres_table,means)
colnames(pres_table)=c("Daily","Weekly")
rownames(pres_table)=c(currencies,"Average")
stargazer(pres_table)
```

Fit ordered lasso
```{r, warning=FALSE,tidy=TRUE, message=FALSE }
#Data type is "daily" or "weekly"
#And curr_i is the currency index
#We use cross validation for parameter selection 
#Returns test error
#p is max lag - we will also optimize over this

lasso_stats=function(data_type,curr_i,p){
  use_data=get(paste(data_type,"_data",sep=""))[[curr_i]]
  #Training x and y 
  train_x=data.matrix(use_data[which(use_data[,"S_train"]==1),"Vol"])
  train_y= data.matrix(use_data[which(use_data[,"S_train"]==1),"Target"])
  #Testing x and y 
  test_x=data.matrix(use_data[which(use_data[,"S_train"]==0),"Vol"])
  test_y=data.matrix(use_data[which(use_data[,"S_train"]==0),"Target"])
  
  #Cross validation model - we enforce strong ordering
  cvmodel=timeLagLasso.cv(train_x,train_y,maxlag=p,strongly.ordered = TRUE,trace=FALSE)
  lam=cvmodel$lamhat
  pred_y = rep(0,length(test_x))
  for(i in 1:length(test_x)){
    x = train_x
    y = train_y
    if(i > 1){
      x = append(x,test_x[1:(i-1)])
      y = append(y,test_y[1:(i-1)])
    }
    model=timeLagLasso(data.matrix(x),data.matrix(y),lambda=lam,maxlag=p,strongly.ordered = TRUE,trace=FALSE)
    pred_y[i] = predict.timeLagLasso(model,test_x[i])[[1]][1]
  }

  #Since we need to also optimize over p we return testing error and training error
  return(c(min(cvmodel$cv.err),mse(pred_y,test_y)))
}

ps=seq(2,6,1)

pos = 1
lasso_results = data.frame(Currency = character(), Type = character(), Lag = numeric(), train_MSE = numeric(), test_MSE = numeric(),  stringsAsFactors = F)
for(type in c('daily','weekly')){
  for(curr_i in 1:length(currencies)){
    for(p in ps){
      temp = lasso_stats(type,curr_i,p)
      lasso_results[pos,] = list(Currency = currencies[curr_i], Type = type, Lag = p, train_MSE = temp[1], test_MSE = temp[2])
      pos = pos + 1
    }
  }
}


#put in presentation form

lasso_results_daily = data.frame(Currency = character(), Lag = numeric(), MSE = numeric(),  stringsAsFactors = F)
lasso_results_weekly = data.frame(Currency = character(), Lag = numeric(), MSE = numeric(),  stringsAsFactors = F)

pos = 1
for(curr in currencies){
  indicies = which(lasso_results$Currency == curr)
  curr_results = lasso_results[indicies,] 
  
  indicies =  which(curr_results$Type == 'daily')
  temp = curr_results[indicies,]
  opt_row = which.min(temp$train_MSE)
  lasso_results_daily[pos,] = list(Currency = curr, Lag = temp$Lag[opt_row], MSE = temp$test_MSE[opt_row])
  #fill weekly
  indicies = which(curr_results$Type == 'weekly')
  temp = curr_results[indicies,]
  opt_row = which.min(temp$train_MSE)
  lasso_results_weekly[pos,] = list(Currency = curr, Lag = temp$Lag[opt_row], MSE = temp$test_MSE[opt_row])
  pos = pos + 1
}



lasso_results_daily[nrow(lasso_results_daily)+1,] = list(Currency = "Average", Lag = '', MSE = mean(lasso_results_daily$MSE)) 
lasso_results_weekly[nrow(lasso_results_daily)+1,] = list(Currency = "Average", Lag = '', MSE = mean(lasso_results_weekly$MSE)) 


stargazer(as.matrix(lasso_results_daily))
stargazer(as.matrix(lasso_results_weekly))

```


Part 2: Incorporate Hidden States

We now turn to the regime switching aspect of things. The following code is VERY time consuming to run - I recommed loaded the already run results located in the data folder. For convenience I put them at the beginning of the code chunk.

Fit the states

```{r, warning=FALSE,tidy=TRUE, message=FALSE }
#Use these unless you want to spend ~4-5 hrs watching code run. 
#setwd("~/Documents/Grad_School/2016-2017_Spring/Amin/Homework/HW_3/FIN580/final/data")
setwd("~/Desktop/FIN580/final/data")
load("Daily_test_regimes_2.RData")
load("Daily_test_regimes_3.RData")
load("Weekly_test_regimes_2.RData")
load("Weekly_test_regimes_3.RData")
load("Daily_states_train_2.RData")
load("Weekly_states_train_2.RData")
load("Daily_states_train_3.RData")
load("Weekly_states_train_3.RData")

setwd("~/Desktop/FIN580_Final")


#This is the actual code used to acquire the results, run at own risk

#Plots and saves HMM on train data for each currency
#We also save the states for tarin only for each model so we can build models for them


plot_hmm_train=function(curr_i,n_states){
  names=c("Regime 1","Regime 2")
  if(n_states>2){
    names=c(names,"Regime 3")
  }
  #Daily
  use_data=daily_data[[curr_i]]
  data=use_data[which(use_data[,"S_train"]==1),]
  hmm=depmix(Vol~1,family=gaussian(),nstates=n_states,data=data)
  hmm_fit=fit(hmm,verbose=FALSE)
  post_probs=posterior(hmm_fit)
  daily_states=data.frame(post_probs$state)
  pdf(paste(currencies[curr_i],n_states,"_TR_daily.pdf",sep="_"), onefile=T, paper='A4r')
  plot(data$Date,post_probs$state, type='s', main='True Regimes - Daily', xlab='', ylab='Regime')
  dev.off()
   pdf(paste(currencies[curr_i],n_states,"_TR_pp_daily.pdf",sep="_"), onefile=T, paper='A4r')
  matplot(post_probs[,-1], type='l', main='Regime Posterior Probabilities - Daily', ylab='Probability')
  legend(x='topright', legend=names, fill=1:n_states, bty='n')
  dev.off()
  
  #Weekly
  use_data=weekly_data[[curr_i]]
  data=use_data[which(use_data[,"S_train"]==1),]
  hmm=depmix(Vol~1,family=gaussian(),nstates=n_states,data=data)
  hmm_fit=fit(hmm,verbose=FALSE)
  post_probs=posterior(hmm_fit)
  weekly_states=data.frame(post_probs$state)
  pdf(paste(currencies[curr_i],n_states,"_TR_weekly.pdf",sep="_"), onefile=T, paper='A4r')
  plot(data$Date,post_probs$state, type='s', main='True Regimes - Weekly', xlab='', ylab='Regime')
  dev.off()
   pdf(paste(currencies[curr_i],n_states,"_TR_pp_weekly.pdf",sep="_"), onefile=T, paper='A4r')
  matplot(post_probs[,-1], type='l', main='Regime Posterior Probabilities - Weekly', ylab='Probability')
  legend(x='topright', legend=names, fill=1:n_states, bty='n')
  dev.off()
  return(list(daily_states,weekly_states))
}

#setwd("~/Documents/Grad_School/2016-2017_Spring/Amin/Homework/HW_3/FIN580/final/plots")

daily_states_2=list()
weekly_states_2=list()
daily_states_3=list()
weekly_states_3=list()
for(i in 1:length(currencies)){
  temp=plot_hmm_train(i,2)
  print(nrow(temp[[1]]))
  daily_states_2[length(daily_states_2)+1]=temp[[1]]
  weekly_states_2[length(weekly_states_2)+1]=temp[[2]]
  temp=plot_hmm_train(i,3)
  print(nrow(temp[[1]]))
  daily_states_3[length(daily_states_3)+1]=temp[[1]]
  weekly_states_3[length(weekly_states_3)+1]=temp[[2]]
}
setwd("~/Desktop/FIN580/data")
#setwd("~/Documents/Grad_School/2016-2017_Spring/Amin/Homework/HW_3/FIN580/final/data")
save(daily_states_2,file="Daily_states_train_2.RData")
save(weekly_states_2,file="Weekly_states_train_2.RData")
save(daily_states_3,file="Daily_states_train_3.RData")
save(weekly_states_3,file="Weekly_states_train_3.RData")



#There is no real "predict" function - instead we use an expanding window to fit an HMM to all the data including the current test value and then we get the final state
#end_i is the end of the testing data set where the current point is
#Since we hope to be able to try both 2 and 3 states, we include n_states as an input for flexibility purposes
#We assume data is Gaussian
get_regime=function(use_data,end_i,n_states){
  #Data getting
  data=use_data[which(use_data[,"S_train"]==1),]
  add=use_data[which(use_data[,"S_train"]==0),]
  add=add[1:end_i,]
  data=rbind(data,add) 
  #Model fitting
  hmm=depmix(Vol~1,family=gaussian(),nstates=n_states,data=data)
  hmm_fit=fit(hmm,verbose=FALSE)
  hmmpost_probs=posterior(hmm_fit)
  return(post_probs$state[length(post_probs$state)])
}

#This function run returns a full set of train states for a currency
get_train_regimes=function(data_type,curr_i,n_states){
  use_data=get(paste(data_type,"_data",sep=""))[[curr_i]]
  train_n=length(use_data[which(use_data[,"S_train"]==0),"Vol"])
  train_regimes=sapply(seq(1,train_n,1),function(x){
    print(x)
    print(currencies[[curr_i]])
    get_regime(use_data,x,n_states)}
    )
  return(train_regimes)
}

daily_test_regimes_2=list()
daily_test_regimes_3=list()
weekly_test_regimes_2=list()
weekly_test_regimes_3=list()
#For some reason can only run 4 sets in the 4 loop (hehe bc it's a four loop get it- but actually it breaks down) then you have to run one by one, don't argue with the computer just give in
for(i in 1:length(currencies)){
  #Daily
  daily_test_regimes_2[length(daily_test_regimes_2)+1]=data.frame(get_train_regimes("daily",i,2))
    daily_test_regimes_3[length(daily_test_regimes_3)+1]=data.frame(get_train_regimes("daily",i,3))
    #Weekly
    weekly_test_regimes_2[length(weekly_test_regimes_2)+1]=data.frame(get_train_regimes("weekly",i,2))
    weekly_test_regimes_3[length(weekly_test_regimes_3)+1]=data.frame(get_train_regimes("weekly",i,3))
}
setwd("~/Desktop/FIN580/data")
#setwd("~/Documents/Grad_School/2016-2017_Spring/Amin/Homework/HW_3/FIN580/final/data")
save(daily_test_regimes_2,file="Daily_test_regimes_2.RData")
save(daily_test_regimes_3,file="Daily_test_regimes_3.RData")
save(weekly_test_regimes_2,file="Weekly_test_regimes_2.RData")
save(weekly_test_regimes_3,file="Weekly_test_regimes_3.RData")

#load("Daily_test_regimes_2.RData")
#load("Daily_test_regimes_3.RData")
#load("Weekly_test_regimes_2.RData")
#load("Weekly_test_regimes_3.RData")

#We also output the number of observations for by states by regime
n_daily=matrix(NA,nrow=3,ncol=2)
rownames(n_daily)=c("Regime 1","Regime 2","Regime 3")
colnames(n_daily)=c("No. States: 2","No. States: 3")
n_weekly=matrix(NA,nrow=3,ncol=2)
rownames(n_weekly)=c("Regime 1","Regime 2","Regime 3")
colnames(n_weekly)=c("No. States: 2","No. States: 3")
for(n in 2:3){
  for(r in 1:2){
    name=paste("daily_test_regimes",n,sep="_")
    temp=get(name)
    denom=sum(sapply(seq(1,length(currencies),1),function(x){return(length(temp[[x]]))}))
    n_daily[r,n-1]=sum(sapply(seq(1,length(currencies),1),function(x){return(length(which(temp[[x]]==r)))}))/denom
    name=paste("weekly_test_regimes",n,sep="_")
    temp=get(name)
    denom=sum(sapply(seq(1,length(currencies),1),function(x){return(length(temp[[x]]))}))
    n_weekly[r,n-1]=sum(sapply(seq(1,length(currencies),1),function(x){return(length(which(temp[[x]]==r)))}))/denom
  }
  if(n>2){
    r=3
    name=paste("daily_test_regimes",n,sep="_")
    temp=get(name)
    denom=sum(sapply(seq(1,length(currencies),1),function(x){return(length(temp[[x]]))}))
    n_daily[r,n-1]=sum(sapply(seq(1,length(currencies),1),function(x){return(length(which(temp[[x]]==r)))}))/denom
    name=paste("weekly_test_regimes",n,sep="_")
    temp=get(name)
    denom=sum(sapply(seq(1,length(currencies),1),function(x){return(length(temp[[x]]))}))
    n_weekly[r,n-1]=sum(sapply(seq(1,length(currencies),1),function(x){return(length(which(temp[[x]]==r)))}))/denom
  }
}

stargazer(n_daily)
stargazer(n_weekly)




```



Step 2: Models by regime. We use the regimes on the training data to fit models on the trading data for each regime. Then we apply the relevant model to the testing data based on the testing regime.

Naming convention for models is as follows: model_d/w_num. of regimes_regime num.

Garch with regime change
```{r,warning=FALSE,tidy=TRUE,message=FALSE}


#Get testing error - average over all currencies
get_garch_test_error=function(data_type,n_states){
  mse=  rep(0,length(currencies))
  for(curr_i in 1:length(currencies)){
    #Getting data
    use_data=get(paste(data_type,"_data",sep=""))[[curr_i]]
    train_ret=use_data[which(use_data[,"S_train"]==1),"Ret"]
    test_ret = use_data[which(use_data[,"S_train"]==0),"Ret"]
    actual_vol= use_data[which(use_data[,"S_train"]==0),"Target"]
    
    #set up state train and test
    states=get(paste(data_type,"states",n_states,sep="_"))[[curr_i]]
    train = cbind(train_ret,states)
    states=get(paste(data_type,"test_regimes",n_states,sep="_"))[[curr_i]]
    test = cbind(test_ret,states)
    
    pred_y = rep(0,length(test_ret))
    for(i in 1:length(test_ret)){
      reg = test[i,2]
      x_train = train[which(train[,2] == reg),1]
      x_test =  test[which(train[1:i,2] == reg),1]
      x = append(x_train,x_test)
      model=garchFit(formula=~garch(1,1),data=x,verbose=FALSE)
      pred_y[i]=  predict(model,n.ahead=1)$standardDeviation
    }
      #Since we have log-vols, but the predictions arent need to change
    pred_y=log(pred_y)
    mse[curr_i] =  mse(pred_y,actual_vol)
  }
    return(mse)
}


mses_daily=matrix(NA,nrow=2,ncol=length(currencies))
mses_weekly=matrix(NA,nrow=2,ncol=length(currencies))

for(n in 2:3){
  mses_daily[n-1,]=get_garch_test_error("daily",n)#,r)
  mses_weekly[n-1,]=get_garch_test_error("weekly",n)#,r)
}

pres_daily=t(mses_daily)
pres_daily=rbind(pres_daily,colMeans(pres_daily))
pres_weekly=t(mses_weekly)
pres_weekly=rbind(pres_weekly,colMeans(pres_weekly))
colnames(pres_daily) = c('2 states','3 states')
rownames(pres_daily) = c(currencies,"Average")
colnames(pres_weekly) = c('2 states','3 states')
rownames(pres_weekly) = c(currencies,"Average")

stargazer(pres_daily)
stargazer(pres_weekly)






```



Ordered Lasso with regime change

```{r, warning=FALSE,tidy=TRUE, message=FALSE }


#helper function to find optimal p, lambda

fit_lasso_regime = function(data_type,curr_i,n_states){
  ps = seq(2,6,1)
  opt_stats = matrix(0,nrow = length(ps),ncol = (1+n_states)) #stores opt lambda for each state and training mse for each p
  rownames(opt_stats) = ps
  names = 'lambda_1'
  for(i in 2:n_states)
    names = c(names, paste('lambda',i,sep = '_'))
  names = c(names,'MSE')
  
  colnames(opt_stats) = c()
  use_data=get(paste(data_type,"_data",sep=""))[[curr_i]]
  train_x = use_data[which(use_data[,"S_train"]==1),"Vol"]
  train_y = use_data[which(use_data[,"S_train"]==1),"Target"]
  
  #set up train
  states=get(paste(data_type,"states",n_states,sep="_"))[[curr_i]]
  train_x = cbind(train_x,states)
    
  #Cross validation model - we enforce strong ordering and find optimal lambda for each regime
  for(p in ps){
    mse = 0
    for(reg in 1:n_states){
        indicies = which(train_x[,2]==reg)
        x = train_x[indicies,1]
        y = train_y[indicies]
        cvmodel=timeLagLasso.cv(data.matrix(x),data.matrix(y),maxlag=p,strongly.ordered = TRUE,trace=FALSE)
        opt_stats[p-1,reg] = cvmodel$lamhat
        mse = mse + cvmodel$cv.err[1] * length(indicies)
      }
      opt_stats[p-1,n_states+1] = mse / nrow(train_x)
  }
  return(opt_stats)
}



#helper function to get statistics for lasso regime fit

lasso_regime_stats=function(data_type,curr_i,n_states,lams_regime,p){
  use_data=get(paste(data_type,"_data",sep=""))[[curr_i]]
  train_x = use_data[which(use_data[,"S_train"]==1),"Vol"]
  train_y = use_data[which(use_data[,"S_train"]==1),"Target"]
  test_x = use_data[which(use_data[,"S_train"]==0),"Vol"]
  test_y = use_data[which(use_data[,"S_train"]==0),"Target"]
  
  #set up state train and test
  states=get(paste(data_type,"states",n_states,sep="_"))[[curr_i]]
  train_x = cbind(train_x,states)
  states=get(paste(data_type,"test_regimes",n_states,sep="_"))[[curr_i]]
  test_x = cbind(test_x,states)
  
  #Cross validation model - we enforce strong ordering and find optimal lambda for each regime
  
  pred_y = rep(0,nrow(test_x))
  for(i in 1:nrow(test_x)){
    reg = test_x[i,2]
    indicies = which(train_x[,2]==reg)
    x = train_x[indicies,1]
    y = train_y[indicies]
    if(i > 1){
      x_sample = matrix(test_x[1:(i-1),],nrow = i-1,ncol = 2)
      y_sample = test_y[1:(i-1)]
      indicies = which(x_sample[,2]==reg)
      x = append(x,x_sample[indicies,1])
      y = append(y,y_sample[indicies])
    }
    
    model=timeLagLasso(data.matrix(x),data.matrix(y),lambda=lams_regime[reg],maxlag=p,strongly.ordered = TRUE,trace=FALSE)
    pred_y[i] = predict.timeLagLasso(model,test_x[i])[[1]][1]
  }
  return(mse(pred_y,test_y))  
}


#fill results
lasso_regime_results = data.frame(Currency = character(), type = character(), n_states = numeric(), p = numeric(), test_mse = numeric(), stringsAsFactors = F)
pos = 1
for(curr_i in 1:length(currencies)){
  for(type in c('daily','weekly')){
    for(n in 2:3){
      temp = fit_lasso_regime(type,curr_i,n)
      p_opt = as.numeric(which.min(temp[,ncol(temp)]))+1
      lam_opt = temp[p_opt-1,1:n]
      mse = lasso_regime_stats(type,curr_i,n,lam_opt,p_opt)  
      lasso_regime_results[pos,] = list(Currency = currencies[curr_i],type = type,n_states = n,p = p_opt,test_mse = mse)
      pos = pos + 1
    }
  }
}


lasso_results_daily_regime2 = data.frame(Currency = character(), Lag = numeric(), MSE = numeric(),  stringsAsFactors = F)
lasso_results_daily_regime3 = data.frame(Currency = character(), Lag = numeric(), MSE = numeric(),  stringsAsFactors = F)
lasso_results_weekly_regime2 = data.frame(Currency = character(), Lag = numeric(), MSE = numeric(),  stringsAsFactors = F)
lasso_results_weekly_regime3 = data.frame(Currency = character(), Lag = numeric(), MSE = numeric(),  stringsAsFactors = F)

for(n in 2:3){
  for(type in c('daily','weekly')){
    pos = 1
    title = paste('lasso_results_',type,'_regime',n,sep='')
    results = get(title)
      
    for(curr in currencies){
      indicies = which(lasso_regime_results$Currency == curr)
      curr_results = lasso_regime_results[indicies,] 
      indicies = which(curr_results$n_states == n)
      curr_results = curr_results[indicies,]
      indicies =  which(curr_results$type == type)
      curr_results = curr_results[indicies,]
      results[pos,] = list(Currency = curr, Lag = curr_results$p, MSE = round(curr_results$test_mse,3))
      pos = pos + 1
    }
    assign(title,results) 
  }
}



#tables for presentation
lasso_results_daily_regime2[nrow(lasso_results_daily_regime2)+1,] = list(Currency = "Average", Lag = '', MSE = mean(lasso_results_daily_regime2$MSE))

lasso_results_daily_regime3[nrow(lasso_results_daily_regime3)+1,] = list(Currency = "Average", Lag = '', MSE = mean(lasso_results_daily_regime3$MSE))

lasso_results_weekly_regime2[nrow(lasso_results_weekly_regime2)+1,] = list(Currency = "Average", Lag = '', MSE = mean(lasso_results_weekly_regime2$MSE))

lasso_results_weekly_regime3[nrow(lasso_results_weekly_regime3)+1,] = list(Currency = "Average", Lag = '', MSE = mean(lasso_results_weekly_regime3$MSE))

stargazer(as.matrix(t(lasso_results_daily_regime2)))
stargazer(as.matrix(t(lasso_results_daily_regime3)))
stargazer(as.matrix(t(lasso_results_weekly_regime2)))
stargazer(as.matrix(t(lasso_results_weekly_regime3)))


```
